\section{Appendix}
\label{sec:appendix}

\paragraph{Organization.}
In this appendix, we provide additional details and descriptions that are not included in the main paper.
Specifically, \S\ref{sec:implementation_details} presents full implementation details including training hyperparameters and prompt templates, and \S\ref{sec:dataset_evaluation_details} provides additional information on datasets and evaluation protocols.

\subsection{Prompt Templates.}
\label{para:prompt_templates}
% The four functions in our method, $\text{Extract}(\vy)$, $\text{QA}(\vc_i)$, $\text{Ans}(\mI, \vv_i)$, and $\gF(\va_i,\, \va_i')$, are implemented via four distinct prompt templates. The specific details of these templates are provided in Appendix~\ref{para:prompt_templates}.

Our reward pipeline consists of four prompts applied to evaluate the factual accuracy of model-generated captions with respect to the input image.
\begin{itemize}
    \item $\text{Extract}(\cdot)$ (\textsc{ClaimExtract}): Extracts verifiable atomic claims explicitly stated in the caption, strictly restricted to color, position, and quantity categories.
    \item $\text{QA}(\cdot)$ (\textsc{ClaimToQA}): Converts each extracted atomic claim into a structured question-answer pair based on predefined formats without reinterpreting the original claim.
    \item $\text{Ans}(\cdot)$ (\textsc{ImageQA}): Answers each generated question directly from the image context, utilizing the original image for reference or a degraded image for quality assessment.
    \item $\gF(\cdot, \cdot)$ (\textsc{AnswerCheck}): Compares the caption-derived answer against the image-grounded answer, allowing simple linguistic variants while enforcing strict semantic checking to produce a binary correctness signal.
\end{itemize}
% (1)~\textsc{ClaimExtract} 
% (2)~\textsc{ClaimToQA} converts each claim into a structured question–answer pair;
% (3)~\textsc{ImageQA} answers each question directly from the image;
% and (4)~\textsc{AnswerCheck} compares the caption-derived answer against the image-grounded answer to produce a binary correctness signal.
% The four prompt templates are provided below.

\input{tables/app_prompts.tex}

\subsection{Implementation Details}
\label{sec:implementation_details}

\paragraph{Training Parameters.}
\label{para:training_parameters}
We train \ours using GRPO~\cite{shao2024deepseekmath} on top of the VeRL framework~\cite{sheng2024hybridflow}.
The key hyperparameters are summarized in Table~\ref{tab:training_params}.

\input{tables/app_training_paras.tex}

\paragraph{Image Augmentation Pipeline.}
\label{para:image_augmentation_pipeline}
To enhance the diversity of training data and improve the model's robustness to visual perturbations, we apply a stochastic image augmentation pipeline to input images during training.
% The pipeline comprises seven augmentation operations, each applied independently with probability $p = 0.125$: \textbf{random resizing} (scale $\in [0.8, 1.2]$), \textbf{brightness adjustment} (factor $\in [0.8, 1.2]$), \textbf{contrast adjustment} (factor $\in [0.8, 1.2]$), \textbf{sharpness adjustment} (factor $\in [0.0, 2.0]$), \textbf{Gaussian blur} (radius $\in [0, 1.0]$), \textbf{Gaussian noise} (intensity $\in [0, 0.05]$), and \textbf{salt-and-pepper noise} (intensity $\in [0, 0.01]$).
Each of the seven augmentation operations is applied independently with probability $p = 0.125$, with parameters drawn uniformly from the specified ranges at runtime. The full configuration is summarized in Table~\ref{tab:aug_pipeline}.
The Figure~\ref{fig:augmented_images} illustrates example augmented images generated by the pipeline.
At each training step, every enabled operation is applied sequentially to the input image with its corresponding probability, yielding a stochastically augmented view while preserving semantic content.
The augmentation parameters are drawn uniformly from the specified ranges at runtime, ensuring sufficient variation across training samples.

\subsection{Dataset and Evaluation Details}
\label{sec:dataset_evaluation_details}
We utilize the VLMEvalKit~\cite{duan2024vlmevalkit} evaluation toolkit for our assessments, and the following sections provide detailed information on the evaluation protocols and datasets employed in our experiments.

\paragraph{Evaluation Protocol.}
All models are served via a local vLLM inference server with tensor parallelism and evaluated using the VLMEvalKit framework.
For open-ended and multiple-choice questions requiring semantic judgment, we employ \texttt{Qwen2.5-32B-Instruct} as the judge model, accessed through a dedicated API endpoint.
Evaluation is conducted in parallel across benchmarks using 64 concurrent API workers (\texttt{--api-nproc 64}) to ensure efficient throughput.
Results are logged and persisted to a designated output directory for reproducibility.

\paragraph{Datasets Statistics.}
Our evaluation suite (v2) comprises 12 benchmarks spanning a diverse range of visual understanding tasks, including perception, reasoning, grounding, and multimodal question answering.
Table~\ref{tab:dataset_stats} summarizes the benchmark names, primary task categories, and the number of evaluation samples for each dataset.
The total evaluation set consists of 74,160 samples across all 12 benchmarks.

\input{tables/app_datasets.tex}

\subsection{Albation Details}

% 图像增强的消融结果
\input{tables/app_image_aug.tex}

% 三个不同组件的消融结果
\input{tables/app_ablation2.tex}

\subsection{Response-Level Self-Verification}
\label{sec:response_level_self_verification}
In addition to the claim-level self-verification described in the main paper, we also explore a response-level self-verification approach where the model evaluates the overall factual accuracy of its generated response with respect to the input image.
Specifically, we design a response-level reward pipeline that directly assesses the correctness of the entire caption without decomposing it into atomic claims.


\input{tables/prompt_selfcheck.tex}
